New approaches for boosting to uniformity

### 2014-10-14 assets/paperdraft/ugb.tex
minor changes

Another approach to obtain uniformity, introduced in this paper, involves defining a more general expression of the AdaBoost criteria:
\begin{equation}
 w_i^{\prime} = w_i \times {\rm exp}\left[-\gamma_i \sum_j a_{ij} p_j\right],
\end{equation}
where $a_{ij}$ are the elements of some matrix $A$\footnote{A natural choice is a square $n\times n$ matrix, but this is not required.}.  For the case where $A$ is the identity matrix, the AdaBoost weighting procedure is recovered.  
Other choices of $A$ will induce non-local effects, {\em e.g.}, consider the sparse matrix $A_{\rm knn}$ given by
\begin{equation}
  a_{ij}^{\rm knn} = \begin{cases} 
    \frac{1}{k}, & j \in \knni, \text{ events $i$ and $j$ belong to the same class} \\
    0, & \text{otherwise},
\end{cases}
\end{equation}
where $\knn(i)$ denotes the set of $k$-nearest-neighbor events to event $i$.
This procedure for updating the event weights, which we refer to as kNNAdaBoost, accounts for the score of each event's $k$ nearest neighbors and not just each event individually.

@@

The gradient-boosting algorithm is general in that it only requires the analyst specify a loss function and its gradient.  The AdaLoss function considers each event individually, but can easily be modified to take into account non-local properties of the classifier as follows:
\begin{equation}
  \label{eq:loss_general}
  L_{\rm general} = \sum\limits_{i=1}^{n} {\rm exp}\left[-\gamma_i \sum\limits_{j} a_{ij} s_j \right]. 
\end{equation} 
For example, the loss function obtained from Eq.~\ref{eq:loss_general} using $A_{\rm knn}$, which we refer to as kNNAdaLoss and denote $L_{\rm knn}$, accounts for the score of each event's $k$ nearest neighbors and not just each event individually.
The pseudo-residuals of $L_{\rm knn}$ are 
\begin{equation}
  -\frac{\partial L_{\rm knn}}{\partial s_k} = \sum\limits_i \gamma_i a_{ik}^{\rm knn} {\rm exp}\left[-\gamma_i \sum_j a_{ij}^{\rm knn} s_j \right].
\end{equation}
One can see that the direction of the gradient will be influenced the most by events whose $k$-nearest-neighbor events are classified poorly. 
We generically refer to GB methods designed to achieve uniform selection efficiency as uniform GB (uGB).  The specific algorithm that uses kNNAdaLoss will be called uGBkNN.

>>>>

Another approach to obtain uniformity, introduced in this paper, involves defining a more general expression of the AdaBoost criteria:
\begin{equation}
 w_i^{\prime} = w_i \times {\rm exp}\left[-\gamma_i \sum_j a_{ij} p_j\right],
\end{equation}
where $a_{ij}$ are the elements of some square matrix $A$.  For the case where $A$ is the identity matrix, the AdaBoost weighting procedure is recovered.  
Other choices of $A$ will induce non-local effects, {\em e.g.}, consider the sparse matrix $A_{\rm knn}$ given by
\begin{equation}
  a_{ij}^{\rm knn} = \begin{cases} 
    \frac{1}{k}, & j \in \knni, \text{ events $i$ and $j$ belong to the same class} \\
    0, & \text{otherwise},
\end{cases}
\end{equation}
where $\knn(i)$ denotes the set of $k$-nearest-neighbor events to event $i$.
This procedure for updating the event weights, which we refer to as kNNAdaBoost, accounts for the score of each event's $k$ nearest neighbors and not just each event individually.

@@

The gradient-boosting algorithm is general in that it only requires the analyst specify a loss function and its gradient.  The AdaLoss function considers each event individually, but can easily be modified to take into account non-local properties of the classifier as follows:
\begin{equation}
  \label{eq:loss_general}
  L_{\rm general} = \sum\limits_{i=1}^{n} {\rm exp}\left[-\gamma_i \sum\limits_{j} a_{ij} s_j \right]. 
\end{equation} 
For example, the loss function obtained from Eq.~\ref{eq:loss_general} using\footnote{A natural choice is a square $n\times n$ matrix, but this is not required.} 
$A_{\rm knn}$, which we refer to as kNNAdaLoss and denote $L_{\rm knn}$, accounts for the score of each event's $k$ nearest neighbors and not just each event individually.
The pseudo-residuals of $L_{\rm knn}$ are 
\begin{equation}
  -\frac{\partial L_{\rm knn}}{\partial s_k} = \sum\limits_i \gamma_i a_{ik}^{\rm knn} {\rm exp}\left[-\gamma_i \sum_j a_{ij}^{\rm knn} s_j \right].
\end{equation}
One can see that the direction of the gradient will be influenced the most by events whose $k$-nearest-neighbor events are classified poorly. 
We generically refer to GB methods designed to achieve uniform selection efficiency as uniform GB (uGB).  The specific algorithm that uses kNNAdaLoss will be called uGBkNN.
